Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-22 cloneoverflow-latex/cloneoverflow.tex
Added missing numbers & fixed the wrong number of cloned projects in ND.
Updated all the numbers after fixing problem of ND clone path. Ready to work on Rocco's comments now.

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter
  315,786,118 detected online clone pairs between 144,064 Java code
  snippets on Stack Overflow and 111 Java open source projects in the
  curated Qualitas corpus. We discovered and investigated 31,946
  non-trivial online clone candidates. Our study revealed that 64 out
  of 112 clones with strong evidence of copying from a Qualitas
  project to Stack Overflow are outdated. Furthermore, we found 357
  code snippets on Stack Overflow that violate the license of their
  original software.
  % These snippets are questionable for reuse.
  % Our study is among the first to address the problem of
  % outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
%Overflow and 111 open source projects from the Qualitas corpus. 
%The Java code snippets were extracted from Stack Overflow posts. 
We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the accuracy of clone detection. Then, we
deployed the two clone detectors to locate clones between the two
datasets.  We partitioned the input and ran the tools multiple
times. Each run was composed of the entire Stack Overflow data and a
single Qualitas project. We repeated the process until we covered all
111 projects.  We then converted the clone reports to the General
Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
single GCF file.  Simian did not provide an option to detect
cross-project clones between two locations. Hence the Simian GCF clone
report was filtered to contain only clone pairs between Stack Overflow
and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas. 
% NiCad provides an option to detect clones
% from two locations so no filtering was needed.

@@

As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
agreement filtering using Bellon's criteria\footnote{Similar to the
  original study, we selected a threshold \textit{t} of 0.7 for both
  \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
of \textit{good} clone pairs is 2,308 and the number of \textit{ok}
clone pairs is 31,729, 0.1\textperthousand~of all reported clone
pairs.  Agreed clone pairs are clone pairs that pass Bellon's
\textit{good} or \textit{ok} criteria, and therefore are selected for
manual classification.  Due to NiCad's failures, we do not have NiCad
clones from five Qualitas projects in the agreed clone pairs. Simian
clones of the same projects also disappeared from the agreed clone
pairs since they could not be matched.

\begin{table}
  \centering
  \caption{Distribution of the agreed clone pairs}
  \label{t_agreed_good_clone_pairs}
  %\small
  %	\resizebox{\columnwidth}{!}{%
  \begin{tabular}{l|r|r|r|r|r}
    \hline
    Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
    \hline
    \textit{good} & 18 & 26 & 10 & 2,267 & 2,308 \\
    \textit{ok} & 11,467 & 993 & 79 & 20,021 & 31,729  \\
    \hline
  \end{tabular} %
  % }
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{good-ok_pairs-crop}
	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
	\label{fig:good-ok-pairs}
\end{figure}

The distribution of \textit{good} clone pairs between the four
combinations of \textit{D} and \textit{E} configurations are listed in
\Cref{t_agreed_good_clone_pairs}.  There are 2,321 (2,308 unique)
\textit{good} pairs consisting of 18 pairs from $S_D$--$N_D$, 26 pairs
from $S_D$--$N_E$, 10 pairs from $S_E$--$N_D$, and 2,267 pairs from
$S_E$--$N_E$. There are 32,560 (31,729 unique) \textit{ok}
pairs\footnote{This excludes the subsumed 2,308 \textit{good}
  pairs. According to the definition, \textit{ok} pairs always subsume
  \textit{good} pairs.}. We obtained 11,467; 993; 79; and 20,021 pairs
from $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, and $S_E$--$N_E$
respectively. Between the four configuration sets, there is
considerable amount of clone pairs shared between two adjacent sets
(as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair
that is agreed by all four combinations.

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{3}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-5}
		& & \textit{L} & \textit{S} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & 88 \\ 
		\hline
		\multicolumn{6}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
	\end{tabular} %
	%}
\end{table}

@@

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the
results using clone size and gook/ok pairs. The
two filters reduced the number of $S_D$ clones to 17,801 pairs. We
filtered $N_D$ clones by additionally raising the similarity
threshold. We increased NiCad's similarity threshold from 70\% to 85\%
(by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We
tried varying the UPI from 70\% (default, 632,855 pairs), 80\%
(25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that
85\% similarity provided the best balance in terms of the amount of
reported clones and precision for small clones. Using this filter
along with the other three filters, we reduced the number of $N_D$
clones to 88 pairs.

@@

For the manual inspection of clone pairs, we selected all
\textit{good} pairs (2,308) and the \textit{ok} pairs for
$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (11,749), but we ignored
20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
their large number of clones and the very small average clone sizes of
5.95 and 6.28 lines (see \Cref{tab:orig_stats}), leading to a high
probability of being trivial clones. We refer to the set of clone
pairs as the \textit{good} set and the \textit{ok'} set.

Together with the 17,801 (referred as $S_D'$ set) and 88 (referred as
$N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
$N_D$, we ended up with a set of 31,946 online clone pair candidates
for manual inspection.

@@

The classification of all 31,946 online clone pairs followed the steps
depicted in \Cref{fig:classification_process}. First, we look at a
pair of clone fragments to see their similarity. If they are
accidentally similar clones after code normalisation or false positive
clones from the clone detection tools, we classify the pair into
\textbf{AC}. If the two fragments are boiler-plate code, the pair is
classified into \textbf{BP}. If they implement the same interface or
inherited the same class and share similar overriding methods, the
pair is classified into \textbf{IN}. If the pair is not \textbf{BP},
\textbf{IN}, or \textbf{AC}, we start a detailed investigation. We
check the corresponding Stack Overflow post, read through it carefully
and look for any evidence mentioning code copying. If evidence of
copying has been found from a Qualitas project, the pair is classified
in \textbf{QS}. In several occasions, we used extra information such
as questions' contents, name of posters, and tags to gain a better
understanding. On the other hand, if the source code from the Qualitas
project mentions copying from Stack Overflow, the pair is classified
into \textbf{SQ}. If there is evidence of copying from an external
source instead of a Qualitas projects, the pair is classified into
\textbf{EX}. Lastly, if there is no evidence of copying in any
direction but the clone fragments are highly similar, we classify them
into \textbf{UD}.

@@

The statistics on clones obtained from the different data sets are
presented in \Cref{tab:snippets}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with all 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 82 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects.  For the cloned Stack Overflow snippets, the
average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
38\%, 50\%, 30\%, and 33\% respectively.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

\begin{table}
\caption{Investigated online clone pairs and corresponding snippets
  and Qualitas projects for the different data sets}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrrr}
  \hline 
  Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
  \hline 
  \multicolumn{4}{l}{\textit{Reported Clones}} \\
  \hline
  $S_D$ & 67,570 & 1,086 & 92 & 38\% \\
  $S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
  $N_D$ & 632,855& 1,392 & 82 & 30\% \\
  $N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
  \hline
  Total & 315,786,118 & &\\
  \hline
  \multicolumn{4}{l}{\textit{Filtered Data Sets}} \\
  \hline
  \textit{good} & 2,308 & 92 & 66 & 23\% \\
  \textit{ok'} & 11,749 & 136 & 39 & 28\% \\
  $S_D'$ & 17,081 & 471 & 76 & 31\% \\
  $N_D'$ & 88 & 77 & 29 & 26\% \\
  \hline
  Total & 31,946 & 621 & 95 & 27\%\\
  \hline 
  \multicolumn{4}{l}{\textit{True Positives without AC}} \\
  \hline 
  $\textit{good}/\textrm{AC}$ & 136 & 47 & 25 & 23\% \\
  $\textit{ok'}/\textrm{AC}$ & 11,644 & 125 & 34 & 28\% \\
  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
  $N_D'/\textrm{AC}$ & 75 & 44 & 17 & 28\% \\
  \hline
  Total & 29,528 & 555 & 81 & 28\% \\
  \hline
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in \Cref{tab:snippets}, for the 2,308
\textit{good} pairs, there are 92 Stack Overflow snippets which are
associated with 66 Qualitas projects. The 11,749 \textit{ok'} pairs
are clones between 136 Stack Overflow snippets and 39 Qualitas
projects.  Moreover, for the disagreed pairs, we found 17,081 clone
pairs reported by $S_D'$ are clones between 471 Stack Overflow
snippets and 76 Qualitas projects and 88 $N_D'$ clone pairs are clones
between 77 Stack Overflow snippets and 29 Qualitas projects. In total
we found that the filtered data sets contains 31,946 clone pairs which
are clones between 621 Stack Overflow snippets and 95 Qualitas
projects. During the manual investigation, we identified 2,418 pairs
as being accidential clones (AC), i.e.~false positives. After removing
them, the data set still contains 29,528 clone pairs between 555 Stack
Overflow snippets and 81 Qualitas projects.

\textbf{To answer RQ1, we found most Qualitas projects to share
  similar code with Stack Overflow code snippets. Depending on the
  data set, between 82 to all 111 projects share similar code. The
  filtered data set has 95 projects share code with Stack
  Overflow. Even in the manually confirmed data set of 29,528 clone
  pairs, a majority of 81 Qualitas projects share similar code with
  Stack Overflow.}

@@

\begin{table}
	\centering
	\caption{No.~of online clones candidates for the classification}
	\label{tab:online_clone_classification_results}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
		& & Auto & Manual \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 \\
		\multirow{1}{*}{\textit{ok'}} & 11,749 & 11,494 & 255 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
		\multirow{1}{*}{$N_D'$} & 88 & 10 & 78 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 31,946 & 28,314 & 3,632 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

We rely on a manual study to qualitatively investigate the patterns of
online code cloning. To achieve this, we classified all 31,946
selected clone pairs according to the process shown in
\Cref{fig:classification_process}.  Before performing the manual
classification, we created and used an automatic classifier 
to classify {\small\texttt{equals()}}, 
{\small\texttt{hashCode()}} and getters/setters. As shown in
\Cref{tab:online_clone_classification_results}, the automatic
classifier helped us to classify 28,314 clone pairs into
pattern \textbf{BP}.

There were 3,632 pairs left for the manual check. The first author,
who has been working on clone detection research for two years, took
the role of the main investigator performing a manual classification
of the 3,632 clone pairs. By consulting the cloning patterns, the main
investigator went through each clone pair candidate, looked at the
clones, and chose the most appropriate cloning pattern for the pair.
%
To mitigate the human errors of the manual classification, the second
author took the role of the validating investigator, performing a
validation on 10\% (363 pairs) of the clone pairs judged by the main
investigator. After the validation, the classifications from the two
investigators were compared and 64 conflicts were found. The two
investigators discussed and resolved 61 of them while the 3 conflicts
were resolved by involving the third author. The classification
results are shown in \Cref{tab:classification_good_o} and explained in
the following.

@@

\textbf{EX: External Sources.} We found 197 online clone pairs with
evidence of cloning from external sources to Stack Overflow. They
include 4, 41, 146, and 6 clone pairs from the \textit{good},
\textit{ok'}, $S_D'$, and $N_D'$ set respectively.

@@

\textbf{UD: Unknown Direction.} We found 382 online clone pairs with
no evidence of cloning between Qualitas and Stack Overflow but with a
high code similarity that suggests cloning. They include 11, 42, 294,
and 35 pairs from the \textit{good}, \textit{ok'}, $S_D'$, and $N_D'$
set respectively. The most cloned projects is \textsf{netbeans} with
95 clone pairs. Most of the clones are a large chunk of code handling
GUI components. Although these GUI clones might be auto-generated by
IDEs, we did not find any evidence. The second most cloned project is
\textsf{jung2} (62 pairs), a network and graph framework, followed by
\textsf{eclipse-SDK} (37 pairs).
% There are several Stack Overflow snippets that are identical to code
% in \textsf{jung2}.

\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate
clone pairs found in this study. Although we have removed some of the
boiler-plate code with filters before the analysis, we still observed
28,749 such clone pairs. The \textbf{BP} clone pairs account for
89.7\% of all clone pairs we classified. The majority of them are
{\small{\texttt{equals()}}} methods.

\textbf{IN: Inheritance/interface.} There were 111 clone pairs found
to be similar because they implement the same interface or inheriting
from the same class. An example is the two implementations of
{\small{\texttt{MouseListener}}} that share similar
{\small\texttt{@Override}} methods of {\small\texttt{mousePressed}},
and {\small\texttt{mouseReleased}}.

\textbf{AC: Accidental Clones.} There were 2,418 accidental clone
pairs. Mainly, they are false positive clones caused by code
normalisation. 
% However, the original source code were still different enough when
% we manually classified them.
Other clone instances include {\small\texttt{finally}} or
{\small\texttt{try-catch}} clauses that were accidentally the same due
to their very small sizes, and similar {\small\texttt{switch-case}}
statements.

>>>>

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter
  315,786,118 detected online clone pairs between 144,064 Java code
  snippets on Stack Overflow and 111 Java open source projects in the
  curated Qualitas corpus. We discovered and investigated 32,533
  non-trivial online clone candidates. Our study revealed that 64 out
  of 112 clones with strong evidence of copying from a Qualitas
  project to Stack Overflow are outdated. Furthermore, we found 357
  code snippets on Stack Overflow that violate the license of their
  original software.
  % These snippets are questionable for reuse.
  % Our study is among the first to address the problem of
  % outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
%Overflow and 111 open source projects from the Qualitas corpus. 
%The Java code snippets were extracted from Stack Overflow posts. 
We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the accuracy of clone detection. Then, we
deployed the two clone detectors to locate clones between the two
datasets. Due to a scalability issue, we partitioned the input and ran the tools multiple
times. Each run was composed of the entire Stack Overflow data and a
single Qualitas project. We repeated the process until we covered all
111 projects.  We then converted the clone reports to the General
Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
single GCF file.  Simian did not provide an option to detect
cross-project clones between two locations. Hence the Simian GCF clone
report was filtered to contain only clone pairs between Stack Overflow
and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas. 
% NiCad provides an option to detect clones
% from two locations so no filtering was needed.

@@

As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
agreement filtering using Bellon's criteria\footnote{Similar to the
  original study, we selected a threshold \textit{t} of 0.7 for both
  \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
clone pairs is 32,316, 0.1\textperthousand~of all reported clone
pairs.  Agreed clone pairs are clone pairs that pass Bellon's
\textit{good} or \textit{ok} criteria, and therefore are selected for
manual classification.  Due to NiCad's failures, we do not have NiCad
clones from five Qualitas projects in the agreed clone pairs. Simian
clones of the same projects also disappeared from the agreed clone
pairs since they could not be matched.

\begin{table}
  \centering
  \caption{Distribution of the agreed clone pairs}
  \label{t_agreed_good_clone_pairs}
  %\small
  %	\resizebox{\columnwidth}{!}{%
  \begin{tabular}{l|r|r|r|r|r}
    \hline
    Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
    \hline
    \textit{good} & 23 & 26 & 10 & 2,267 & 2,313 \\
    \textit{ok} & 12,336 & 993 & 79 & 20,021 & 32,316 \\
    \hline
  \end{tabular} %
  % }
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{good-ok_pairs}
	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
	\label{fig:good-ok-pairs}
\end{figure}

The distribution of \textit{good} clone pairs between the four
combinations of \textit{D} and \textit{E} configurations are listed in
\Cref{t_agreed_good_clone_pairs}.  There are 2,326 (2,313 unique)
\textit{good} pairs consisting of 23 pairs from $S_D$--$N_D$, 26 pairs
from $S_D$--$N_E$, 10 pairs from $S_E$--$N_D$, and 2,267 pairs from
$S_E$--$N_E$. There are 33,156 (32,316 unique) \textit{ok}
pairs\footnote{This excludes the subsumed 2,313 \textit{good}
  pairs. According to the definition, \textit{ok} pairs always subsume
  \textit{good} pairs.}. We obtained 12,336; 993; 79; and 20,021 pairs
from $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, and $S_E$--$N_E$
respectively. Between the four configuration sets, there is
considerable amount of clone pairs shared between two adjacent sets
(as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair
that is agreed by all four combinations.

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{3}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-5}
		& & \textit{L} & \textit{S} & \textit{G} & \\
		\hline 
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & 83 \\ 
		\hline
		\multicolumn{6}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
	\end{tabular} %
	%}
\end{table}

@@

As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the
results using clone size and gook/ok pairs. The
two filters reduced the number of $S_D$ clones to 17,801 pairs. We
filtered $N_D$ clones by additionally raising the similarity
threshold. We increased NiCad's similarity threshold from 70\% to 85\%
(by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We
tried varying the UPI from 70\% (default, 632,855 pairs), 80\%
(25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that
85\% similarity provided the best balance in terms of the amount of
reported clones and precision for small clones. Using this filter
along with the other three filters, we reduced the number of $N_D$
clones to 83 pairs.

@@

For the manual inspection of clone pairs, we selected all
\textit{good} pairs (2,313) and the \textit{ok} pairs for
$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (12,336), but we ignored
20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
their large number of clones and the very small average clone sizes of
5.95 and 6.28 lines (see \Cref{tab:orig_stats}), leading to a high
probability of being trivial clones. We refer to the set of clone
pairs as the \textit{good} set and the \textit{ok'} set.

Together with the 17,801 (referred as $S_D'$ set) and 83 (referred as
$N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
$N_D$, we ended up with a set of 32,533 online clone pair candidates
for manual inspection.

@@

The classification of all 32,533 online clone pairs followed the steps
depicted in \Cref{fig:classification_process}. First, we look at a
pair of clone fragments to see their similarity. If they are
accidentally similar clones after code normalisation or false positive
clones from the clone detection tools, we classify the pair into
\textbf{AC}. If the two fragments are boiler-plate code, the pair is
classified into \textbf{BP}. If they implement the same interface or
inherited the same class and share similar overriding methods, the
pair is classified into \textbf{IN}. If the pair is not \textbf{BP},
\textbf{IN}, or \textbf{AC}, we start a detailed investigation. We
check the corresponding Stack Overflow post, read through it carefully
and look for any evidence mentioning code copying. If evidence of
copying has been found from a Qualitas project, the pair is classified
in \textbf{QS}. In several occasions, we used extra information such
as questions' contents, name of posters, and tags to gain a better
understanding. On the other hand, if the source code from the Qualitas
project mentions copying from Stack Overflow, the pair is classified
into \textbf{SQ}. If there is evidence of copying from an external
source instead of a Qualitas projects, the pair is classified into
\textbf{EX}. Lastly, if there is no evidence of copying in any
direction but the clone fragments are highly similar, we classify them
into \textbf{UD}.

@@

The statistics on clones obtained from the different data sets are
presented in \Cref{tab:snippets}. Simian in the default configuration
($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
144,064 Stack Overflow snippets, associated with 92 Qualitas
projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
snippets containing clones associated with all 111 Qualitas
projects. NiCad in the default configuration ($N_D$) reported clones
between 1,392 Stack Overflow code snippets and 88 Qualitas
projects. NiCad in the EvaClone configuration ($N_E$) reported the
largest number of 12,886 cloned snippets mainly due to the more
relaxed configuration. The $N_E$ snippets are associated with 88
Qualitas projects.  For the cloned Stack Overflow snippets, the
average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
38\%, 50\%, 30\%, and 33\% respectively.
% A quick manual check of Simian's clone report revealed that there
% were 11 problematic snippets. These 11 snippets triggered Simian to
% generate large clone clusters containing a huge number of false
% clones from array initialisation. Hence, their clones were removed
% from further analyses.

@@

\begin{table}
\caption{Investigated online clone pairs and corresponding snippets
  and Qualitas projects for the different data sets}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrrr}
  \hline 
  Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
  \hline 
  \multicolumn{5}{l}{\textit{Reported Clones}} \\
  \hline
  $S_D$ & 67,570 & 1,086 & 92 & 38\% \\
  $S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
  $N_D$ & 632,855& 1,392 & 88 & 30\% \\
  $N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
  \hline
  Total & 315,786,118 & 14,856 & 111 & 38\% \\
  \hline
  \multicolumn{5}{l}{\textit{Filtered Data Sets}} \\
  \hline
  \textit{good} & 2,313 & 97 & 67 & 23\% \\
  \textit{ok'} & 12,336 & 139 & 43 & 28\% \\
  $S_D'$ & 17,081 & 460 & 74 & 31\% \\
  $N_D'$ & 83 & 44 & 19 & 27\% \\
  \hline
  Total & 32,533 & 623 & 96 & 27\%\\
  \hline 
  \multicolumn{5}{l}{\textit{True Positives without AC}} \\
  \hline 
  $\textit{good}/\textrm{AC}$ & 141 & 52 & 26 & 23\% \\
  $\textit{ok'}/\textrm{AC}$ & 12,229 & 126 & 36 & 28\% \\
  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
  $N_D'/\textrm{AC}$ & 70 & 39 & 16 & 29\% \\
  \hline
  Total & 30,113 & 556 & 80 & 28\% \\
  \hline
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in \Cref{tab:snippets}, for the 2,313
\textit{good} pairs, there are 97 Stack Overflow snippets which are
associated with 67 Qualitas projects. The 12,336 \textit{ok'} pairs
are clones between 139 Stack Overflow snippets and 43 Qualitas
projects.  Moreover, for the disagreed pairs, we found 17,081 clone
pairs reported by $S_D'$ are clones between 460 Stack Overflow
snippets and 74 Qualitas projects and 83 $N_D'$ clone pairs are clones
between 44 Stack Overflow snippets and 19 Qualitas projects. In total
we found that the filtered data sets contains 32,533 clone pairs which
are clones between 623 Stack Overflow snippets and 96 Qualitas
projects. During the manual investigation, we identified 2,420 pairs
as being accidential clones (AC), i.e.~false positives. After removing
them, the data set still contains 30,113 clone pairs between 556 Stack
Overflow snippets and 80 Qualitas projects.

\textbf{To answer RQ1, we found most Qualitas projects to share
  similar code with Stack Overflow code snippets. Depending on the
  data set, between 88 to all 111 projects share similar code. The
  filtered data set has 96 projects share code with Stack
  Overflow. Even in the manually confirmed data set of 30,113 clone
  pairs, a majority of 80 Qualitas projects share similar code with
  Stack Overflow.}

@@

\begin{table}
	\centering
	\caption{No.~of online clones candidates for the classification}
	\label{tab:online_clone_classification_results}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
		& & Auto & Manual \\
		\hline 
		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
		\hline
		Total  & 32,533 & 28,897 & 3,636 \\ 
		\hline
	\end{tabular} %
	%}
\end{table}

We rely on a manual study to qualitatively investigate the patterns of
online code cloning. To achieve this, we classified all 32,533
selected clone pairs according to the process shown in
\Cref{fig:classification_process}.  Before performing the manual
classification, we created and used an automatic classifier 
to classify {\small\texttt{equals()}}, 
{\small\texttt{hashCode()}} and getters/setters. As shown in
\Cref{tab:online_clone_classification_results}, the automatic
classifier helped us to classify 28,897 clone pairs into
pattern \textbf{BP}.

There were 3,636 pairs left for the manual check. The first author,
who has been working on clone detection research for two years, took
the role of the main investigator performing a manual classification
of the 3,636 clone pairs. By consulting the cloning patterns, the main
investigator went through each clone pair candidate, looked at the
clones, and chose the most appropriate cloning pattern for the pair.
%
To mitigate the human errors of the manual classification, the second
author took the role of the validating investigator, performing a
validation on 10\% (364 pairs) of the clone pairs judged by the main
investigator. After the validation, the classifications from the two
investigators were compared and 64 conflicts were found. The two
investigators discussed and resolved 61 of them while the 3 conflicts
were resolved by involving the third author. The classification
results are shown in \Cref{tab:classification_good_o} and explained in
the following.

@@

\textbf{EX: External Sources.} We found 200 online clone pairs with
evidence of cloning from external sources to Stack Overflow. They
include 4, 44, 146, and 6 clone pairs from the \textit{good},
\textit{ok'}, $S_D'$, and $N_D'$ set respectively.

@@

\textbf{UD: Unknown Direction.} We found 359 online clone pairs with
no evidence of cloning between Qualitas and Stack Overflow but with a
high code similarity that suggests cloning. They include 15, 20, 293,
and 31 pairs from the \textit{good}, \textit{ok'}, $S_D'$, and $N_D'$
set respectively. The most cloned projects is \textsf{netbeans} with
93 clone pairs. Most of the clones are a large chunk of code handling
GUI components. Although these GUI clones might be auto-generated by
IDEs, we did not find any evidence. The second most cloned project is
\textsf{jung2} (62 pairs), a network and graph framework, followed by
\textsf{eclipse-SDK} (37 pairs).
% There are several Stack Overflow snippets that are identical to code
% in \textsf{jung2}.

\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate
clone pairs found in this study. %Although we have removed some of the
%boiler-plate code with filters before the analysis, we still 
We observed 29,330 such clone pairs. The \textbf{BP} clone pairs account for
90\% of all clone pairs we classified. The majority of them are
{\small{\texttt{equals()}}} methods.

\textbf{IN: Inheritance/interface.} There were 112 clone pairs found
to be similar because they implement the same interface or inheriting
from the same class. An example is the two implementations of
{\small{\texttt{MouseListener}}} that share similar
{\small\texttt{@Override}} methods of {\small\texttt{mousePressed}},
and {\small\texttt{mouseReleased}}.

\textbf{AC: Accidental Clones.} There were 2,420 accidental clone
pairs. Mainly, they are false positive clones caused by code
normalisation. 
% However, the original source code were still different enough when
% we manually classified them.
Other clone instances include {\small\texttt{finally}} or
{\small\texttt{try-catch}} clauses that were accidentally the same due
to their very small sizes, and similar {\small\texttt{switch-case}}
statements.
